Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-05-08 Manuscript/detrendify_aoas.tex
editing figures for defense presentation

\section{Acknowledgments}
The authors greatly appreciate Eben Thoma at the US Environmental Protection Agency for providing the SPod datasets. The authors are also thankful for the Oak Ridge Institute of Science Fellowship that partially supported this work. Plots were created using ggplot2 \citep{ggplot2}.

@@

	\item[R-package for detrend routine:] R-package detrendr containing code to perform the methods described in the article. (GNU zipped tar file also available at https://github.com/halleybrantley/detrendr)

>>>>

\section{Acknowledgments}
The authors greatly appreciate Eben Thoma at the U.S. Environmental Protection Agency for providing the SPod datasets. This work was supported by the National Science Foundation under grant No. 1613219 and the National Institutes of Health under grant No. R01ES027892. The authors are also thankful for the Oak Ridge Institute of Science Fellowship that supported this work. Plots were created using ggplot2 \citep{ggplot2}.

\noindent {\large\bf Disclaimer}
The views expressed in this publication are those of the authors and do not represent the views or policies of the U.S. Environmental Protection Agency.

@@

	\item[R-package for detrend routine:] R-package detrendr containing code to perform the methods described in the article (GNU zipped tar file). Package is also available at \url{https://github.com/halleybrantley/detrendr}.
